Rates of true polar wander in convecting planets

### 2014-09-30 tpw_rate.tex
TEXT

%\documentclass[extra,onecolumn]{gji}
\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\begin{figure}
\centering
\label{misfit}
\includegraphics[width=20cm]{figures/eigengap.pdf}
\caption{Oooga}
\end{figure}

\begin{figure}
\centering
\label{misfit}
\includegraphics[width=10cm]{figures/perturb.pdf}
\caption{Oooga}
\end{figure}

@@

Furthermore, the quantity $(\lambda_i-\lambda_j)$ which appears in the denominator is precisely the same as the quantity which we estimated in the previous section to be $\sim \mathrm{Ra}^{-1}$.
Therefore, as the Rayleigh number increases, the characteristic gap between the eigenvalues of the convective moment becomes smaller.  
Additionally, the timescale of fluctuations in these values goes down. 
Overall, this makes the principle axes of high Rayleigh number systems much less stable.
This result agrees with the qualitative results of

\begin{figure}
\centering
\label{misfit}
\includegraphics[width=20cm]{figures/misfit.pdf}
\caption{Oooga}
\end{figure}

@@

>>>>

\documentclass[extra,onecolumn]{gji}
%\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\begin{figure}
\centering
\label{misfit}
\includegraphics[width=0.9\textwidth]{figures/eigengap.pdf}
\caption{Oooga}
\end{figure}

\begin{figure}
\centering
\label{misfit}
\includegraphics[width=0.9\textwidth]{figures/perturb.pdf}
\caption{Graphical demonstration of the $\sin{2 \theta}$ theorem of \citet{davis1970rotation}.  Two spheroidal bodies with eigenvalues $\lambda_2 > \lambda_1$ start out with the rotation axis $\Omega$ aligned with the $\lambda_2$ axis. However, on the left the eigengap $\lVert \lambda_2 - \lambda_1 \rVert$ is large, while on the right it is small.  A perturbation is instantaneously added to both bodies, which effects a small rotation of the principle axes on the left, but a large one on the right.}
\end{figure}

@@

Furthermore, the quantity $(\lambda_i-\lambda_j)$ which appears in the denominator is precisely the same as the quantity which we estimated in the previous section to scale with $\sim \mathrm{Ra}^{-1}$.
Therefore, as the Rayleigh number increases, the characteristic gap between the eigenvalues of the convective moment becomes smaller.  
Additionally, the timescale of fluctuations in these values goes down. 
Overall, this makes the principle axes of high Rayleigh number systems much less stable.
This result is consistent with the result of \citet{richards1997explanation}.

\begin{figure}
\centering
\label{misfit}
\includegraphics[width=0.9\textwidth]{figures/misfit.pdf}
\caption{Top: }
\end{figure}

@@

We have developed a framework for discussing the rates of true polar wander in terms of a small number of nondimensional numbers.
